\documentclass[a4paper,12pt]{article}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{titling}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{hyperref}

\geometry{
  left=1in,
  right=1in,
  top=1in,
  bottom=1in
}
\setstretch{1.3}

\begin{document}

% ---------- COVER PAGE ----------
\begin{titlepage}
    \centering
    \vspace*{2cm}

    {\Huge \bfseries Information Theory in Biology \par}
    \vspace{1.5cm}

    {\Large \textbf{Course: 13 Information Theory in Biology}\par}
    \vspace{2.5cm}

    {\large \textbf{}\\[0.5cm]
    Aanchal Mundhada \hfill 2023112016\\
    Sanjana Sheela \hfill 2023102027\\
    Pragnya Tatiparthi \hfill 2023102067\\
    Parth Tokekar \hfill 2023102041\\[2cm]}

    {}\par

    \vfill

    {\large \textbf{Under the Supervision of}\\[0.3cm]
    Dr. Indranil Chakrabarty\\
    Associate Professor\\
    Centre for Quantum Science and Technology (CQST), IIITH
    }
\end{titlepage}




% ---------- INDEX ----------
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage

% ---------- MAIN CONTENT ----------
\pagenumbering{arabic}

\section{Introduction}
Brief introduction to Information Theory and its relevance in biological systems.

\section{Historical Background}
Discuss Shannon’s foundational work and how it influenced the study of biological communication.

\section{Genetic Information and DNA Encoding}
How biological systems store, process, and transmit genetic information.

\section{Neural Information Processing}
Information-theoretic approaches to studying neurons, entropy, and signaling pathways.

\section{Evolutionary Information Theory}
How information theory explains adaptation, mutation, and selection in evolution.

\section{Applications in Modern Biology}
Use in genomics, protein folding, and systems biology.

\section{Conclusion}
Summarize the findings and relevance of information theory to biology.

\section{References}
% Example:
% \begin{thebibliography}{9}
% \bibitem{shannon1948}
% C. E. Shannon, "A Mathematical Theory of Communication", Bell System Technical Journal, 1948.
% \end{thebibliography}

\end{document}
